Paper without a name

### 2014-05-30 Article.tex
Changes..

We can easily determine trivial lower and upper bounds of the number of
boxes~:\\ Given the fact that $C$ is an application, we need to have
$Card(\{0;1\}^{k}) \geq Card(\mathfrak{S}_n)$. We immediately obtain that $k$
has to be greater than $\log_2(n!)$.\\ We also have an upper bound~: The
traditional bubblesort gives a valid configuration of the SwitchBoxes problem. We
obtain that the optimal $k$ is smaller than $\frac{(n-1)(n-2)}{2}$.

@@

In a second step, we show how we proved this conjecture for $n$ from 2 to 6, and
how we demonstrated that the number of comparisons is an upper bound of the
optimal number of boxes for $n$ from 7 to 13 by optimizing the checking
algorithm and by constructing a precise configuration.

@@

For greater values of $n$, we implemented a naive and brutal algorithm that for
$k$ given, creates all the possible configurations of $k$ boxes, and checks if
one of these configurations is valid. We first try it with $opt_{n-1}+1$. Then,
we increment $k$ and try again until we get a valid configuration.  With this
algorithm, we easily get $opt_n$.\\
However, this only works for small values of $n$. For $n$ greater than 6, we
lack memory and time to achieve the computation.

@@

\begin{figure}
    \centering
    \begin{tabular}{|c|c|}
    \hline
    Number of wires $n$ & $opt_n$ \\
    \hline
    2 & 1 \\
    3 & 3 \\
    4 & 5 \\
    5 & 8 \\
    6 & 11 \\
    \hline
    \end{tabular}
    \caption{Minimum box count for small number of wires}
    \label{box-count}
\end{figure}

@@

\Large
\begin{Conj*}
$opt_n$ is equal to the maximal number of comparisons for sorting $n$ elements
by binary insertion.
\end{Conj*}
\normalsize

>>>>

We can easily determine trivial lower and upper bounds of the number of
boxes~:\\ Given the fact that $C$ is an application, we need to have
$Card(\{0;1\}^{k}) \geq Card(\mathfrak{S}_n)$. We immediately obtain that $k$
has to be greater than $\log_2(n!)$.\\ We also have a reachable upper bound~: The
traditional bubblesort gives a valid configuration of the SwitchBoxes problem. We
obtain that the optimal $k$ is smaller than $\frac{(n-1)(n-2)}{2}$.

@@

In a second step, we show how we experimentally this conjecture for $n$ from 2 to 6, and
how we demonstrated that the number of comparisons is an upper bound of the
optimal number of boxes for $n$ from 7 to 13 by optimizing the checking
algorithm and by constructing a precise configuration.

@@

For greater values of $n$, we implemented a naive and brutal algorithm that for
$k$ given, creates all the possible configurations of $k$ boxes, and checks if
one of these configurations is valid. We first try it with $k = opt_{n-1}+1$. Then,
we increment $k$ and try again until we get a valid configuration.  With this
algorithm, we easily get $opt_n$.\\
However, this only works for small values of $n$. For $n$ greater than 6, we
lack memory and time to achieve the computation.

@@

\begin{figure}
    \centering
    \begin{tabular}{|c|c|}
    \hline
    Number of wires $n$ & $opt_n$ \\
    \hline
    2 & 1 \\
    3 & 3 \\
    4 & 5 \\
    5 & 8 \\
    6 & 11 \\
    \hline
    \end{tabular}
    \caption{Minimum box count for small number of wires, checked experimentally}
    \label{box-count}
\end{figure}

@@

\begin{Conj*}
$opt_n$ is equal to the maximal number of comparisons for sorting $n$ elements
by binary insertion.
\end{Conj*}
